Can Symmetric Cryptography Be Liberated from the Von Neumann Style?

### 2024-10-12 paper.tex
Rephrase

  In defiance of Hinchliffe's rule, this article sets out to
  demonstrate that its title can be answered by the word ``yes''. We
  show that modern symmetric ciphers can be modeled through a small
  set of algebraic structures (Boolean algebra, Naperian and foldable
  functors). We reveal that these ciphers exhibit some interesting
  compositional structure at the type-level, which enables systematic
  code transformation, known in the cryptographic folklore as
  ``bitslicing'' and ``fixslicing''. Our work rests on a Coq
  development providing the specification of two ciphers, Skinny and
  Gift, deriving a bitsliced and fixsliced implementation for each and
  proving their correctness with respect to their specifications.

>>>>

  In defiance of Hinchliffe's rule, this article sets out to
  demonstrate that its title can be answered by the word ``yes''. We
  show that modern symmetric ciphers can be modeled through a small
  set of algebraic structures (Boolean algebra, Naperian and foldable
  functors). We reveal that these ciphers exhibit some interesting
  compositional structure at the type-level. This enables systematic
  code transformation, known in the cryptographic folklore as
  ``bitslicing'' and ``fixslicing''. Our work rests on a Coq
  development providing the specification of two ciphers, Skinny and
  Gift, deriving a bitsliced and fixsliced implementation for each and
  proving their correctness with respect to their specifications.
